\documentclass{resume} 
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{hyperref} 
\hypersetup{
	colorlinks=true,  
	urlcolor=cyan,
}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Raidel Nápoles} % Your name
\address{Software Engineer} 

\begin{document}
	\begin{rSection}{Contact}
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			phone & (+53) 53026190\\
			email & \href{mailto:raidelnapoles95@gmail.com}{raidelnapoles95@gmail.com} \\
			address & Havana, Cuba\\
			linkedin & \href{https://www.linkedin.com/in/raidel-napoles} {linkedin.com/in/raidel-napoles}\\
			github & \href{https://github.com/RaidelNapoles} {RaidelNapoles}
		\end{tabular}
		
	\end{rSection}
	
	
	\begin{rSection}{Work experience}
		\begin{rSubsection}{Geocuba}{May 2019 - present}{Backend Developer}{}
			\item Research on the calculation of optimal routes on maps
				\subitem (SqLite, SpatiaLite, Postgres, PostGis, Mapserver, JavaScript)
			\item Backend Developer for the systems: 
				\subitem Identification system for the population and housing census 
					\subsubitem(JavaScript, Express, Node.js)
				\subitem Management and control system for scientific activity
					\subsubitem(TypeScript, NestJS, Node.js, PostgreSQL)
		\end{rSubsection}
	
		\begin{rSubsection}{National Institute of Sports, Physical Education, and Recreation}{ December 2020 - present}{Fullstack Software Developer}{}
			\item Frontend Developer on INDER's photographic repository website 
				\subitem(HTML, CSS).
			\newline	
			\item Fullstack Software Developer on INDER's journalistic publications website 
				\subitem(Python/Django, PostgreSQL, HTML, CSS).
		\end{rSubsection}
		
		\begin{rSubsection}{Rimycs (freelance development team)}{ August 2022 - August 2023}{Backend Developer}{}
			\item Development of a platform for money remittances
			\subitem(TypeScript, NestJS, Node.js, MongoDb, Consuming third-party services).
			
		\end{rSubsection}
	
		\begin{rSubsection}{Codeberry Solutions}{ October 2023 - February 2024}{Backend Developer}{}
			\item Development of a resume creation platform.
			\subitem(TypeScript, NestJS, Node.js, PostgreSQL, Stripe).
			
		\end{rSubsection}
		
		\begin{rSubsection}{SmartAnalytics}{ February 2024 - present}{Fullstack Software Developer}{}
			\item Fullstack programmer in the development of an assisted information search platform
			\subitem(Python, Django, Javascript, HTML, CSS).
			\item Fullstack programmer in the development of a legal advice platform
			\subitem(Python, Django, Javascript, HTML, CSS).
			\item Fullstack programmer in the development of a legal assistance platform
			\subitem(Python, Django, Javascript, HTML, CSS).
			
		\end{rSubsection}	
		
	\end{rSection}

	
	\begin{rSection}{Personal - Freelancer Projects}
		\begin{rSubsection}{Mobile app developer}{}{}
			\item  App (apk) InfoPyME
			(\href{https://apklis.cu/application/com.napper.infopyme21}{https://apklis.cu/application/com.napper.infopyme21})
			\subitem (Kotlin, XML, Python, SQL)
		\end{rSubsection}	
	\end{rSection}
	
	
	\begin{rSection}{Education}
		{\bf University of Havana} \hfill {\em 2014 - 2020} 
		\\ Bachelor in Computer Science. \hfill {\em 2020}
	\end{rSection}
	
	
	\begin{rSection}{Skills}
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
		Programming Languages \ & Python, JavaScript, TypeScript, , Kotlin, Java  \\
		Frameworks & NestJS, Django, Node.js, Express, React \\
		Databases & SQLite, MySQL, PostgreSQL\\
		Version Management & Git, GitLab, Github\\
		Others & Problem-solving skills, Teamwork, Time management
		\end{tabular}
	\end{rSection}
	
	
	\begin{rSection}{Language Skills}
		\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
			Mother tongue & Spanish\\
			Other language(s) & English (B1 level)
		\end{tabular}
	\end{rSection}

\end{document}
